Refunctionalization of Abstract Abstract Machines (Functional Pearl)

### 2018-04-15 paper/paper.tex
Update the code using delimited control

\begin{lstlisting}
def analyze(e: Expr) = {
  def iter(cache: Cache): Ans = {
    reset {
      val Ans(vss, anscache) = aeval(e, Map[String, BAddr](), Store[BAddr, Storable](Map()), List(), cache)
      val initConfig = Config(e, Map[String, BAddr](), Store[BAddr, Storable](Map()), List())
      val new_cache = anscache.outUpdate(initConfig, vss)
      if (new_cache.out == cache.out) { Ans(vss, new_cache) }
      else { iter(Cache(new_cache.out, new_cache.out)) }
    }
  }
  iter(mtCache)
}
\end{lstlisting}

>>>>

\begin{lstlisting}
val mtEnv = Map[String, BAddr]()
val mtStore = Store[BAddr, Storable](Map())
val mtTime = List()

def analyze(e: Expr) = {
  def iter(cache: Cache): Ans = {
    val Ans(vss, anscache) = reset { aeval(e, mtEnv, mtStore, mtTime, cache) }
    val initConfig = Config(e, Map[String, BAddr](), Store[BAddr, Storable](Map()), List())
    val new_cache = anscache.outUpdate(initConfig, vss)
    if (new_cache.out == cache.out) { Ans(vss, new_cache) }
    else { iter(Cache(new_cache.out, new_cache.out)) }
  }
  iter(mtCache)
}
\end{lstlisting}
